|

### 2018-12-19 Paper 2019.Rmd
Adding old paper for history

*Add CCI summary* 
<!--clean these up--> 
```{r CCI summary}
descr(convictions)
# Barber histograms 
convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
convictions.plot
```

>>>>

*Add CCI summary* 
<!--clean these up--> 
```{r CCI summary}
descr(convictions)
convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
convictions.plot
# FAIL convictions.time <- ggplot(convictions, aes(Year,CCI)) + stat_summary(fun.y = sum) + theme_minimal()
```
